### 2022-01-07 paper/issta22/abstract.tex
intro

\begin{abstract}

  Evaluating natural language model (\Nlp) on testset does with
  held-out accuracy is limited to show its quality assurance because
  the held-out datasets are often not comprehensive. While the
  behavioral testing over multiple general linguistic capabilities are
  employed, it relies on manually created test cases, and is still
  limited to measure its comprehensive performance for each linguistic
  capability. In this work, we introduce \OurModelName, an \Nlp model
  testing methodology. Given a linguistic capability, The
  \OurModelName finds relevant testcases to test the linguistic
  capability from extisting datasets as seed inputs, generates
  sufficient number of new test cases by fuzzing the seed inputs based
  on their context-free grammar (\Cfg). We illustrate the usefulness
  of the \OurModelName by showing input diversity and identifying
  critical failures in \sota models for \Nlp task. In our experiment,
  we show that the \OurModelName generates {} more test cases with {}
  higher diversity, and finds {} more bugs.

>>>>

\begin{abstract}
  \Nlp (NLP) technique becomes one of the core techniques for developing
  text analytics applications.  For developing the NLP applications,
  the applications are required to achieve high reliability before it
  goes to market.  The trustworthiness of the prevalent NLP
  applications is obtained by measuring the accuracy of the
  applications on held-out dataset.  However, evaluating NLP on
  testset does with held-out accuracy is limited to show its quality
  because the held-out datasets are often not comprehensive. While the
  behavioral testing over multiple general linguistic capabilities are
  employed, it relies on manually created test cases, and is still
  limited to measure its comprehensive performance for each linguistic
  capability. In this work, we introduce \OurModelName, an NLP model
  testing methodology. Given a linguistic capability, The
  \OurModelName finds relevant testcases to test the linguistic
  capability from existing datasets as seed inputs, generates
  sufficient number of new test cases by fuzzing the seed inputs based
  on their context-free grammar (\Cfg). We illustrate the usefulness
  of the \OurModelName by showing input diversity and identifying
  critical failures in \sota models for NLP task. In our experiment,
  we show that the \OurModelName generates {} more test cases with {}
  higher diversity, and finds {} more bugs.

### 2022-01-07 paper/issta22/intro.tex
intro

\Nlp testing is crucial part for developing a reliable \Nlp model. In
\Nlp, testing is mainly used to check the ML model's performance on
\ho set with respect to the accuracy of the model. The \ho data refers
to a portion of dataset that is held out of the datasets used for
training \ml models. Generally, the \ho set is extracted via
Train-Validation-Test split.

>>>>

Software testing is the cruicial process when developing software.  It
evaluates an attribute or capability of the software and determines
that it meets the requirements by examining the behavior of the
software under test. Software testing in the early stage of the
development finds bugs, and fixing them saves amount of costs. In
addition, reliable software testing methodology ensures software
quality to users in that the software meets requirements by
verification and validation. Regarding that, testing NLP application
becomes important process as well in that NLP application is a branch
of artifical intelligence software.

Prevalent NLP model is evaluated via train-validation-test
splits. train and validation set is used to train the NLP model and
the \ho set is used for testing by measuring accuracy

testing \ml becomes major

\Nlp testing is crucial part for developing a reliable \Nlp
applications. For developing \Nlp applications, testing is mainly used
to check the ML model's performance on \ho set with respect to the
accuracy of the model. The \ho data refers to a portion of dataset
that is held out of the datasets used for training \ml
models. Generally, the \ho set is extracted via Train-Validation-Test
split.
